Assessing the Firing of Ceramic Materials: a Seriation-Based Approach

### 2023-08-01 analysis/paper/paper.qmd
Update changelog

| **Version** | **Date**   | **Description**            | **DOI** |
|---------:|-----------:|:------------------------------|:---------------------------|
| 1.0      | 2023-06-09 | Submitted to _Archéosciences_ | [10.5281/zenodo.8020137](https://doi.org/10.5281/zenodo.8020137) |
| 1.1      | 2023-08-01 | Corrections based on reviews  | |

>>>>

| **Version** | **Date**   | **Description**            | **DOI** |
|---------:|-----------:|:------------------------------|:---------------------------|
| 1.0      | 2023-06-09 | Submitted to _Archéosciences_ | [10.5281/zenodo.8020138](https://doi.org/10.5281/zenodo.8020138) |
| 1.1      | 2023-08-01 | Corrections based on reviews  | [10.5281/zenodo.8204409](https://doi.org/10.5281/zenodo.8204409) |
